\clearpage
\phantomsection
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENT}
\thispagestyle{footeronly}

\begin{center}
{\Large \textbf{ACKNOWLEDGEMENT}}
\end{center}

\justifying
\noindent
First and foremost, we offer our deepest gratitude and humble prayers to the Almighty, whose grace and blessings have been our guiding light throughout this project. We express our heartfelt appreciation to our esteemed Project Guide, Ms. Amrutha S Nair, for her invaluable guidance, unwavering patience, and continued support throughout the development of ProblySUS, her insightful feedback and encouragement were instrumental in shaping the successful implementation of this project. We also extend our sincere thanks to our Project Coordinator, Ms. Sheena S, for her constructive guidance and constant support during every phase of our work, and to Mr. Pramod Pavithran, Head of the Department, for his leadership and direction that kept our project on the right path. We remain truly grateful to our friends and classmates for their helpful suggestions, cooperation, and motivation throughout the development process, as their involvement played a vital role in refining our ideas and execution. Last but not least, we would like to express our profound gratitude to our families for their endless encouragement, understanding, and moral support, without which this accomplishment would not have been possible.

\vspace{1.5cm}
\noindent
Midhun M (20223070)\\
Muhammed Faaz Razi (20223072)\\
Muhammed Irfan E (20223073)\\
Muhammed Sahal (20223074)\\
Nidal CMP (20223077)\\

\vfill
\clearpage