\begin{thebibliography}{10}

\bibitem{ref1}
I. Corona, G. Giacinto, and F. Roli,
``Adversarial attacks against intrusion detection systems: Taxonomy, solutions and open issues,''
\textit{Information Sciences}, vol. 239, pp. 201--225, 2013.

\bibitem{ref2}
M. A. Rajab, L. Ballard, N. Jagpal, P. Mavrommatis, D. Nojiri, N. Provos, and L. Schmidt,
``Trends in circumventing web-malware detection,''
Google Technical Report, 2011.

\bibitem{ref3}
M. Lison and J. Tiedemann,
``OpenNMT: Open-source toolkit for neural machine translation,''
in \textit{Proc. ACL 2016 System Demonstrations}, Berlin, Germany, 2016.

\bibitem{ref4}
N. Chou, R. Ledesma, Y. Teraguchi, and J. C. Mitchell,
``Client-side defense against web-based identity theft,''
in \textit{Proc. 11th Annual Network and Distributed System Security Symposium (NDSS)}, San Diego, CA, USA, 2004.

\bibitem{ref5}
F. Roesner, T. Kohno, and D. Wetherall,
``Detecting and defending against third-party tracking on the web,''
in \textit{Proc. 9th USENIX Symposium on Networked Systems Design and Implementation (NSDI)}, San Jose, CA, USA, 2012, pp. 155--168.

\bibitem{ref6}
A. Oest, Y. Safaei, A. Doupe, G. J. Ahn, B. Wardman, and G. Warner,
``Inside a phisher's mind: Understanding the anti-phishing ecosystem through phishing kit analysis,''
in \textit{Proc. APWG Symposium on Electronic Crime Research (eCrime)}, 2018.

\bibitem{ref7}
S. Dhalwani and S. Khan,
``A survey on URL-based phishing detection techniques using machine learning,''
\textit{International Journal of Computer Applications}, vol. 975, p. 8887, 2020.

\bibitem{ref8}
Abuse.ch,
``URLhaus --- A project with the goal of sharing malicious URLs,''
[Online]. Available: \texttt{https://urlhaus.abuse.ch}.  
[Accessed: March 2026].

\bibitem{ref9}
Microsoft Playwright Team,
``Playwright: Fast and reliable end-to-end testing for modern web apps,''
[Online]. Available: \texttt{https://playwright.dev}.  
[Accessed: March 2026].

\bibitem{ref10}
G. Acar, C. Eubank, S. Englehardt, M. Juarez, A. Narayanan, and C. Diaz,
``The web never forgets: Persistent tracking mechanisms in the wild,''
in \textit{Proc. 2014 ACM SIGSAC Conference on Computer and Communications Security (CCS)}, Scottsdale, AZ, USA, 2014, pp. 674--689.

\end{thebibliography}